Data Preparation

### 2019-01-10 Data Preparation.Rmd
text: tidy text format

We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

>>>>

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)
